\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{fontawesome}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}


\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

\hypersetup{%
    pdfborder = {0 0 0}
}
% END RESUME DEFINITIONS %

\begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Dhruv Sujatha}}\\
	\href{https://www.google.com/maps/place/West+Lafayette,+IN/}{West Lafayette, IN} $\cdot$ \href{mailto:dsujatha@purdue.edu}{dsujatha@purdue.edu} $\cdot$ (765) 746-9702 $\cdot$ \href{https://dsujatha.xyz}{dsujatha.xyz} $\cdot$ \href{https://www.linkedin.com/in/dhruvsujatha/}{\faLinkedinSquare \hspace{2pt} dhruvsujatha} $\cdot$ \href{https://github.com/dhruvsujatha}{\faGithub \hspace{2pt} dhruvsujatha}\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Purdue University}\hfill \textbf{\textit {West Lafayette, IN}}\\
Bachelor\textquotesingle{}s of Science - Computer Science \hfill \textbf{\textit {Expected Graduation: May 2025}}\\
Bachelor\textquotesingle{}s of Science - Data Science \hfill \textbf{\textit{GPA: 3.5}}\\
\vspace{1mm}
\textbf{Coursework:} Object-Oriented Programming: CS180, Discrete Mathematics: CS182, C-Programming: CS240, Introduction to Data Science: CS242, Statistics for Data Science: STAT355\\
\vspace{1mm}
\textbf{Planned (Spring 2023)}: Data Structures and Algorithms: CS251, Computer Architecture: CS250, Probability: STAT416\\
\vspace{1mm}
\textbf{Proficient Languages:} Python 3.x, C, Java, C++, R, SQL
\vspace{1mm}\\
%==== Professional Experience ====%
\header{Professional Experience}

\textbf{Rosen Center for Advance Computing (ITaP)} \hfill \textbf{\textit {West Lafayette, IN}}\\
\textit{Student High Performance Computing Engineer} \hfill \textbf{\textit {January 2022 - Present}}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Responsible for the planning, inventorying, deployment, and maintenance of 9 supercomputing clusters on campus.
    Developed pipelines to automate cluster management tasks such as logging and monitoring. 
\end{itemize}
\begin{tabular}{ l l }
    \underline{\textbf {Skills Developed:}} \href{https://www.python.org/}{Python}, \href{https://www.gnu.org/software/bash/}{Bash Scripting}, \href{https://docs.netbox.dev/en/stable/}{NetBox}, Redfish, \href{https://xcat.org/}{xCAT}, \href{https://slurm.schedmd.com/overview.html}{SLURM}, \href{https://asana.com/}{Asana} 
\end{tabular} \\ 
\vspace{1mm}
\textbf{Farfetch - The DataMine} \hfill \textbf{\textit {West Lafayette, IN}}\\
\textit{Data Science Researcher} \hfill \textbf{\textit {August 2021 - May 2022}}\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked with a team of students researchers via The DataMine Learning Community to store, analyze, and interpret fashion data to develop a Deep Neural Network model to predict size and fit.
    Gained valuable experience in the use of Agile Software Development methodologies and related tools such as Asana, Trello, and Jira.
\end{itemize}
\vspace{-1mm}
\begin{tabular}{ l l }
    \underline{\textbf {Skills Developed:}} \href{https://www.python.org/}{Python}, \href{https://www.tensorflow.org/}{Tensorflow}, \href{https://scikit-learn.org/stable/index.html}{Sci-Kit Learn}, \href{https://pandas.pydata.org/}{Pandas}, \href{https://www.mysql.com/}{MySQL}, \href{https://trello.com/}{Trello}, \href{https://jira.atlassian.com/}{Jira}
\end{tabular} \\ 
\vspace{2mm}

%==== Other Experience ====%
\header{Other Experience}
\textbf{Student Cluster Competition - SC 2022} \hfill \textbf{\textit {November 2022 - Dallas, TX}}\\
\vspace{-2mm}
\begin{itemize}
    \item Part of the SCC team representing Purdue University and Indiana University at the Supercomputing Conference 2022. 
    Worked on the development of a mini supercomputing cluster capable of running scalable HPC applications such as PHASTA and LAMMPS. 
    Optimized and compiled state of the art benchmarks such as HPL, HPCG, and MLPerf. Created a dynamic power management interface to monitor and control the power consumption of the cluster by underclocking and limiting the GPUs and CPUs.\\
\end{itemize}
\vspace{-1mm}
\begin{tabular}{ l l }
    \underline{\textbf {Skills Developed:}} \href{https://www.cplusplus.com/}{C++}, \href{https://www.kernel.org/}{Linux Kernel}, \href{https://www.python.org/}{Python}, \href{https://www.gnu.org/software/bash/}{Bash Scripting}, Spack, \href{https://www.open-mpi.org/}{OpenMPI}, \href{https://developer.nvidia.com/cuda-zone}{CUDA}, \href{https://git-scm.com/}{Git}
\end{tabular}\\
\vspace{1mm}
{\textbf{Autonomous Robotics Club of Purdue}} \hfill \textbf{\textit {January 2022 - West Lafayette, IN}}\\
\textit{Server Admin Team}
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Part of the Server Administrator Team responsible for the upkeep of the technical stack used by all the projects at ARC.
    Worked on deploying the infrastructure for the ARC website and the ARC Discord server using Docker.
\end{itemize}
\begin{tabular}{ l l }
    \underline{\textbf {Skills Developed:}} \href{https://www.python.org/}{Python}, \href{https://www.gnu.org/software/bash/}{Bash Scripting}, \href{https://www.docsy.dev/}{Docsy}, \href{https://gohugo.io/about/what-is-hugo/}{Hugo}, \href{https://www.docker.com/}{Docker}, \href{https://www.proxmox.com/en/}{ProxMox}
\end{tabular} \\
\vspace{1mm}
\textit{Piano Hand Project - Software Team Lead}
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Leading the software team to develop a serial API to control a biomechanical hand to play the piano. Using deep learning frameworks to train a model which can recognize music to dynamically control the hand.\\
\end{itemize}
\vspace{-1mm}
\begin{tabular}{ l l }
    \underline{\textbf {Skills Developed:}} \href{https://cplusplus.com/}{Arduino C}, \href{https://micropython.org/}{MicroPython}, \href{https://mosquitto.org/}{Mosquitto}
\end{tabular} \\
\vspace*{2mm}

\header{Certifications and Awards}
\textbf{ASA Datafest 2022} \hfill \textbf{\textit{American Statistical Association}}\\
\vspace {1mm}
$\cdot$ Recognized by the American Statistical Association for my work in finding meaning \hfill \textbf{\textit {March 2022}}\\ from a large and complex data set to aid in data-driven decisions. \\
\vspace{2mm}
\textbf{AITP Computing Challenge Day 2022} \hfill \textbf{\textit{Association of Information Technology Professionals}}\\
\vspace {1mm}
$\cdot$ First in the \textit{ITaP Super Computing Challenge} where we had to optimize rendering of a \hfill \textbf{\textit {April 2022}}\\ simulation of our universe utilizing ffmpeg, OpenMPI, and Intel MPI. 
\vspace{2mm}\\
$\cdot$ First in the \textit{DataMine ML Challenge} where we had to derive the conditional probabilities\\ of target features in a dataset and visualize it as a graph.
\vspace*{6.94mm}

\end{document}