\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Dhruv Sujatha}}\\
	\href{https://www.google.com/maps/place/West+Lafayette,+IN/}{West Lafayette, IN} $\cdot$ \href{mailto:dsujatha@purdue.edu}{dsujatha@purdue.edu} $\cdot$ (765) 746-9702 $\cdot$ \href{https://dsujatha.xyz}{dsujatha.xyz}\\
\end{center}

\hrulefill
\fontsize{14pt}{17pt}\selectfont

\vspace*{30pt}
Hiring Manager\\
Databricks\\

\vspace*{30pt}

Dear Hiring Manager,\\
\vspace*{20pt}
Thank you for the opportunity to apply for the Data Science Intern role at Databricks. 
I am a sophomore at Purdue University currently pursuing a Bachelor of Science in Computer Science and Data Science.
I have always been a strong believer in the power of data and the ability of machine learning to solve real-world problems. 
My fascination with computers and the analytical problem solving method is deep rooted, has led me to pursue my current major.
I believe that my specific skillset in Data Science and experience make me a strong candidate for this position.

\vspace*{20pt}

I have a strong background in Machine Learning and Data Science, 
and I am proficient in Python, R, and SQL. I have experience working with large datasets
involving data cleaning and data visualization using Pandas, Matplotlib, and Plotnine, and predictive modeling of machine learning 
and deep learning models such as Prod2Vec, Recurrent Neural Networks, and Convolutional Neural Networks with Farfetch as a part of The DataMine learning community as a Student Researcher. \\

\vspace*{20pt}

I have a strong scripting background with python and am comfortable with using the linux command line from my experience as a part-time Student HPC Engineer 
at the Rosen Center of Advance Computing (RCAC) at Purdue University.
I am also familiar with the software development life cycle like Agile and have experience working with version control systems such as Git. \\
I have also worked extensively with the Azure suite of tools in building pipelines and workflows using Continuous Integration and Continuous Deployment stacks like Jenkins.\\

\vspace*{20pt}

Thank you for your consideration, and I look forward to hearing from you soon.

\vspace*{20pt}

Sincerely,\\
Dhruv Sujatha\\
\end{document}